Updated Ephemerides of the young multi-planet system V1298 Tau from TESS

### 2021-10-18 src/ms.tex
end of day updates

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0 0}]{TESSaperture.pdf}
\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band. There are two bight nearby sources to \sname. However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible. \label{fig:tpf}}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

@@

\section{Analysis} \label{sec:analysis}
To model the TESS photometry we used \exoplanet, an open-source Python package for probabilistic inference of exoplanet properties from time series data using gradient descent \citep{exoplanet2019, exoplanet2021}.\begin{deluxetable}{l r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{\sname light curve fitting results. \label{tab:table}}
\tablehead{\colhead{Planets} & \colhead{c} & \colhead{d} & \colhead{b} & \colhead{e} \\
\hline\
P [days]               &  &  &  &  \\
$T_0$ [BJD - 2457000]  &  &  &  &  \\
Depth [ppt]            &  &  &  &  \\
$R_p/R_\star$          &  &  &  &  \\
$a/R_\star$            &  &  &  &  \\
$b$                    &  &  &  &  \\
$e$ [$^\circ$]         &  &  &  &  
}
\startdata
\enddata
%\tablecomments{}
\end{deluxetable}

@@

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{folded_compare.pdf}
\caption{Phase-folded transits comparing the transit depth observed with \textit{K2} (gray) and \tess\ (color) with residuals from the best-fit model (solid line) underneath. Gaps in the data are due to other planets' transits being masked. \label{fig:compare}}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band. \sname is shown in the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's. There are two bight nearby sources to \sname. However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible. \label{fig:tpf} }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Analysis} \label{sec:analysis}
We simultaneously modeled the transits of \allplanets and the stellar variability using the open-source packages \exoplanet \citep{exoplanet2019, exoplanet2021} and \texttt{PyMC3} \citep{Salvatier16}. Transit timings were originally identified using updated ephemerides from \textit{Spitzer} (Livingston et al. in prep). All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black). The residuals between the data and each fit are shown underneath. The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete. \label{fig:compare}}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{deluxetable*}{l r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{\sname light curve fitting results. \label{tab:table}}
\tablehead{\\
\hline\
\textit{Star} & \textit{Value} & \textit{Prior} &  & \\
\hline\
$M_\star [M_\odot]$ & & & & \\
$R_\star [R_\odot]$ & & & & \\
$u_1$ & & & & \\
$u_2$ & & & & \\
$P_{rot}$ [days] & & & & \\
ln($A$ [ppt]) & & & & \\
ln($Q_0$) & & & & \\
$\Delta Q_0$ & & & & \\
f [ppt] & & & & \\
mix & & & & \\
\hline\
\textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
\hline\
P [days]               &  &  &  &  \\
$T_0$ [BJD - 2457000]  &  &  &  &  \\
Depth [ppt]            &  &  &  &  \\
$R_p/R_\star$          &  &  &  &  \\
$a/R_\star$            &  &  &  &  \\
$b$                    &  &  &  &  \\
$e$ [$^\circ$]         &  &  &  &  \\
\hline\
\textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
\hline\
log($P$ [days]) & & & & \\
$T_0$ [BJD - 2457000] & & & & \\
log($R_p/R_\oplus$) & & & & \\
$b$ & & & & \\
$e$ & & & & \\
$\omega$ [$^\circ$] & & & & 
}
\startdata
\enddata
%\tablecomments{}
\end{deluxetable*}
